Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane

### 2021-04-28 paper/paper.tex
A method to time stuff on hosts at last?
More principled t'put for hosts.

\section{Design and Implementation}\label{sec:design}
Based on the design principles, problems, and potential solutions outlined throughout \cref{sec:motivation}, we present our design for an in-NIC, task-independent, online reinforcement learning system---\emph{\approachshort{} (\approach)}.
At a high level, \approachshort{} is designed to use the auxiliary compute exposed by general SmartNIC devices to offer low-latency online learning, scaling according to available on-chip resources at build time.

@@

Policy sizes are set to those matching a real-world DDoS control application~\parencite{DBLP:journals/tnsm/SimpsonRP20}: 20-dimension state vectors, a bias tile and 16 full tiling sets (7$\times$1-dim, 8$\times$2-dim, 1$\times$4-dim), 8 tilings per dimension set, 6 tiles per dimension, choosing between 10 actions.

@@

\begin{table}
\caption{NFP memory use due to \approachshort{} using \numlist{1;4} MEs (\SI{32}{\bit}). CLS and CTM regions are shared between all programs on the same island (placing our RL agent on i5), while EMEM and IMEM regions are shared between all NFP programs on a NIC.\label{tab:resources}}
\resizebox{\linewidth}{!}{
\begin{tabular}{@{}cSSSSSSSSSS@{}}
	\toprule Firmware & \multicolumn{2}{c}{EMEM} & \multicolumn{2}{c}{EMEM Cache} & \multicolumn{2}{c}{IMEM} & \multicolumn{2}{c}{i5.CLS} & \multicolumn{2}{c}{i5.CTM}\\
	& \multicolumn{1}{c}{\si{\mebi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} \\
	\midrule Base P4 & 6776.67 & 88.24 & 268.52 & 2.91 & 858.28 & 10.48 & 0 & 0 & 0 & 0 \\
	\Indfw(1) & 6778.77 & 88.27 & 1738.01 & 18.86 & 1263.28 & 15.42 & 23.50 & 36.72 & 90.00 & 35.16 \\
	\Indfw(4) & 6778.79 & 88.27 & 1746.88 & 18.95 & 1263.28 & 15.42 & 49.00 & 76.56 & 90.00 & 35.16 \\
	\Coopfw(1) & 6778.76 & 88.27 & 1742.51 & 18.91 & 1263.28 & 15.42 & 19.66 & 30.72 & 90.00 & 35.16 \\
	\Coopfw(4) & 6778.76 & 88.27 & 1738.04 & 18.86 & 1263.28 & 15.42 & 31.82 & 49.71 & 90.00 & 35.16 \\
	\bottomrule
\end{tabular}
}
\end{table}

>>>>

\section{Design and Implementation}\label{sec:design}
?? Can we say ``in-situ'' anywhere? I like that term.

Based on the design principles, problems, and potential solutions outlined throughout \cref{sec:motivation}, we present our design for an in-NIC, task-independent, online reinforcement learning system---\emph{\approachshort{} (\approach)}.
At a high level, \approachshort{} is designed to use the auxiliary compute exposed by general SmartNIC devices to offer low-latency online learning, scaling according to available on-chip resources at build time.

@@

Policy sizes are set to those matching a real-world DDoS control application~\parencite{DBLP:journals/tnsm/SimpsonRP20}: 20-dimension state vectors, a bias tile and 16 full tiling sets (7$\times$1-dim, 8$\times$2-dim, 1$\times$4-dim), 8 tilings per dimension set, 6 tiles per dimension, choosing between 10 actions.
Although their more successful \emph{SPF} agent design uses 4 actions, we choose this to investigate the performance of larger agent designs.

@@

\begin{table}
\caption{NFP memory use due to \approachshort{} using \numlist{1;4} MEs (\SI{32}{\bit}). CLS and CTM regions are shared between all programs on the same island (placing our RL agent on i5), while EMEM and IMEM regions are shared between all NFP programs on a NIC.\label{tab:resources} ??NEEDS REWORKED}
\resizebox{\linewidth}{!}{
\begin{tabular}{@{}cSSSSSSSSSS@{}}
	\toprule Firmware & \multicolumn{2}{c}{EMEM} & \multicolumn{2}{c}{EMEM Cache} & \multicolumn{2}{c}{IMEM} & \multicolumn{2}{c}{i5.CLS} & \multicolumn{2}{c}{i5.CTM}\\
	& \multicolumn{1}{c}{\si{\mebi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} & \multicolumn{1}{c}{\si{\kibi\byte}} & \multicolumn{1}{c}{\si{\percent}} \\
	\midrule Base P4 & 6776.67 & 88.24 & 268.52 & 2.91 & 858.28 & 10.48 & 0 & 0 & 0 & 0 \\
	\Indfw(1) & 6778.77 & 88.27 & 1738.01 & 18.86 & 1263.28 & 15.42 & 23.50 & 36.72 & 90.00 & 35.16 \\
	\Indfw(4) & 6778.79 & 88.27 & 1746.88 & 18.95 & 1263.28 & 15.42 & 49.00 & 76.56 & 90.00 & 35.16 \\
	\Coopfw(1) & 6778.76 & 88.27 & 1742.51 & 18.91 & 1263.28 & 15.42 & 19.66 & 30.72 & 90.00 & 35.16 \\
	\Coopfw(4) & 6778.76 & 88.27 & 1738.04 & 18.86 & 1263.28 & 15.42 & 31.82 & 49.71 & 90.00 & 35.16 \\
	\bottomrule
\end{tabular}
}
\end{table}
